Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/appendix.tex
typo

\subsection{\code{TraversableOnce} Trait from Scala Standard Library}
Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~ref{sec:collex}.

>>>>

\subsection{\code{TraversableOnce} Trait from Scala Standard Library}
Figure~\ref{fig:traversableonce} presents the code from Scala's \code{TraversableOnce} trait discussed in Section~\ref{sec:collex}.
